#Austrailian_Marriage_Law_Response_Only
---
title: "Assignment1-Prince-Austrailia Marriage Law Survey Response"

author:Tamia Prince

date: 11/March/2021

output: html_document

---


**Data Source**

We're going to examine Austrailia's Marriage Law Postal 
Survey Response from the 2017 Austrailian Bureau of Statistics.
_Why?_

**Background**

* Starting in 2004 to 2017 there were 22 inefficacious attempts 
to legalize same sex marraige in Federal Parliment. 

* In 2017 this survey was conducted and did not need to be approved 
by parliment, which meant those who wanted there vote to be heard 
had a fighting chance.

* This survey was upheld by the high court.

* The results of this survey determined whether the same sex marriage 
bill was passed. 

* The results conclude that 61.6% of respondents said yes on the 
survey so the same sex marriage bill was passed.

**Characteristics**

_DataType_: Survey reponse records (In numbers and Percentages)

_Columns_: Yes, No, Response clear, Response not clear(a),
Non-responding, Total 

_Rows_: Places in Austrailia

**Variables**

'Yes' and 'No' are used for variables in terms of their 
percentage and response count. 

_(Below is the data in it's raw form)_

```{r}
rm(list = ls())
#install.packages("readxl")
library("readxl")
dataframe <- read_excel("/Users/Tamia/C:/CIS8392/Austrailian_Marriage_Law_Postal_Survey_2017_-_Response_final.xls")
dataframe

```
**Why is the data not tidy?**

The data is not tidy because it has empty NA values, 
and spaces between columns. The merged columns cause 
problems with interpretation, and there is a link and 
extra text around the data as well. Columns needed renaming 
to help define what the values mean and to better see which 
each title without the extra information at the top and bottom. 

```{r}
#install.packages("testthat")
#install.packages("assertive")
#install.packages("rlang")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("readxl")
library(readxl)
library(tidyverse)
library(rvest)

path = "Austrailian_Marriage_Law_Postal_Survey_2017_-_Response_final.xls"
response_counts <-
  read_excel(
    path,
    range = "A8:P20",
    col_name = c( "Place",
                  "Yes",
                  "Yes_percentage",
                  "No",
                  "No_percentage",
                  "Total_Response",
                  "Total_Response_percentage",
                  "blank",
                  "Response_clear",
                  "Response_clear_percentage",
                  "Response_not_clear(b)",
                  "Response_not_clear(b)_percentage",
                  "Non-responding",
                  "Non-responding_percentage",
                  "Eligible_Total",
                  "Eligible_Total_percentage")
  ) %>%
  select(-blank) %>%
  drop_na() %>%
  mutate(Place = gsub("\\([a-z]\\)","",Place)) %>%
  filter(!grepl("Total", Place))

knitr::kable(response_counts)

```
**Why is the data now tidy?**

The data is now tidy because The titles of the columns are 
rightfully assigned. There is no extra text or footnotes in 
the data. The column and row titles are clearly defined. The 
empty column in between the data is gone so it looks like one 
whole dataset together. The merged cells have been split to 
reflect the needed titles of the data. I also got rid of the 
lower case letter using the mutate function. Lastly I only 
kept the rows that showed survey values for each Place, so 
there is only valuable data in the dataset. 

```{r dataframe}
library(ggplot2)
ggplot(response_counts, aes(x=No, y=Yes)) + geom_point() + geom_smooth()
```
**Line Graph GGPLOT**


This plot show a line graph in the a direct relationship 
between the number of yes and no responses. 
The pattern in this plot is as the Yes votes increase, 
so do the No votes.
It is meaningful because it shows that there was an increasing 
number of votes casted for both choices. 

```{r}
#install.packages("ggplot2")

library(ggplot2)
bar = ggplot(response_counts, mapping = 
               aes(x =No, y =Yes)) + geom_boxplot() + coord_flip()
bar

```
**Bar Graph GGPLOT**


This plot shows a bar chart for the repondant's answers.
The pattern in this plot shows that slighty more 
people voted 'Yes' than 'No'. 
It is meaningful because it shows that the deviation of 
the 'Yes' votes from the No votes is prevalent but not significant. 

